Self Regulation Ontology Retest Data Report

### 2017-04-23 SRO_Report.Rmd
got bootstrapping to work locally

bootstrap_relialibility(dv_var = numeric_cols[1])

>>>>

as.data.frame(numeric_cols) %>%
  mutate(index = 1:n()) %>%
  group_by(index) %>%
  # rowwise()%>% #this works too but the output is nicer the other way
  do(plyr::rdply(2, bootstrap_relialibility(dv_var = as.character(.$numeric_cols), metric = c("icc", "spearman"))))
